Learning how to act: making good decisions with machine learning

### 2017-09-07 thesis/offcuts.tex
adds minor fixes up to start of 2211

>>>>

\subsection{Fairness and Ethics}
Causal graphical models are not enough. A causal graph that is correct in the sense that it accurately predicts the outcome of an intervention, does not capture how that intervention could turn out in an alternate world in which implicit bias and discrimination did not exist. As is well understood in economics, we can get a local minima in which individuals and companies are acting rationally (for example by not hiring women) but the consequence for society as a whole is worse.

### 2017-09-07 thesis/offcuts_chapter6.tex
adds minor fixes up to start of 2211

\chapter*{Todo}
\begin{enumerate}
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (across viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}

@@

>>>>

\chapter*{Todo}
\begin{enumerate}
\item Write a talk - include slide on causal inference without do
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (across viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}

@@

\section{Conclusion}

Ideas developed within the off-policy selection liturature are also relevent classic causal problems within economics etc.
 - optimal action selection (rather than evaluation)
 - quantification of finite time properties of estimators (as opposed to asymptopic efficiency). eg \cite{}

Most of the underlying applications do involve decisions which are in fact made sequentially (or in sequential batches). Even if a fully online system is impractical, the underlying concepts of the exploration/exploitation trade-off

That is a principled, yet very broadly applicable strategy to select model parameters in the absense of strong theory

While theoretical bounds are extremely important and much work remains to be done in this area, particularly on finite time bounds, it is very difficult to obtain tig

We do not have sufficent theory to give tight finite time bounds on the quality of complex estimation technqiues for causal estimation (or supervise
